---
title: "R Notebook"
output: html_notebook
---

This is an attempt to apply Kejriwal and Perron test which is implemented in the R `strucchange` package to find cointegration breakpoints. For cointegrated time series used classic example - GLD & GDX.


```{r}
library(tseries)
library(quantmod)
library("strucchange")

from <- "2006-05-23"
to <- "2008-07-23"
tickerArray <- c("GLD", "GDX")
getSymbols(tickerArray, from = from, to = to)

data <- cbind(Cl(GLD), GDX$GDX.Adjusted)
data <- data[complete.cases(data)]
names(data) <- c("GLD", "GDX")
model <- lm(GLD ~ GDX, data)

coint.res <- residuals(lm(GLD ~ GDX, data))
```

Source data charts
```{r}
layout(matrix(1:2, ncol=1))
candleChart(GLD, multi.col = TRUE, theme = 'white', layout=NULL, TA=NULL)
candleChart(GDX, multi.col = TRUE, theme = 'white', layout=NULL, TA=NULL)
```

Check for cointegration
```{r}
print(adf.test(coint.res, k = 0))
```

p-value is small so GLD & GDX in the date range 2006-05-23 ... 2008-07-23 cointegrated. Cointegration charts of Source data
```{r}
layout(matrix(1:3, ncol=1))
plot(GLD ~ GDX, data)
abline(model)
plot(coint.res, type = "l")
plot(as.vector(Cl(GLD)), col = 'blue', type = 'l', main = 'Cointegration GLD & GDX', ylab = 'price')
lines(as.vector(GDX$GDX.Adjusted * coef(model)[2]+coef(model)[1]), col = 'red', type = 'l')
```

Now lets extend date range to 2006-05-23 ... 2009-07-23 and check for cointegration

```{r}
from <- "2006-05-23"
to <- "2009-07-23"
tickerArray <- c("GLD", "GDX")
getSymbols(tickerArray, from = from, to = to)

data <- cbind(Cl(GLD), GDX$GDX.Adjusted)
data <- data[complete.cases(data)]
names(data) <- c("GLD", "GDX")
model <- lm(GLD ~ GDX, data)

coint.res <- residuals(lm(GLD ~ GDX, data))
print(adf.test(coint.res, k = 0))
```

p-value is not small so we cannot assure that GLD & GDX cointegrated in the 2006-05-23 ... 2009-07-23 date range. Ok let's try to find breaking dates. breakpoints() worked on one time serie. So for using breakpoint() function for finding breakpoints in cointegration let's use residuals of GLD&GDX Linear regression model. I expect that after finding breakpoints adf.test for every segment will be small so on every segment GLD & GDX will be cointegrated

```{r}
breakpoints(coint.res ~ 1)
```

Let's check adf.test for 1st interval 1:165 
```{r}
coint.res <- residuals(lm(GLD ~ GDX, data[1:165]))
print(adf.test(coint.res, k = 0))
```

On the 1st segment p-value is not small. So we cannot assure that on the 1st segment GLD & GDX cointegrated. And hence we cannot use Kejriwal and Perron test which is implemented in the R `strucchange` package for finding cointegration breakpoints